\documentclass[9pt]{extarticle}

\usepackage[utf8]{inputenc}
\usepackage[colorlinks=true,urlcolor=linkcolor]{hyperref}
\usepackage[default,scale=0.95]{opensans} % Add this line for OpenSans


% Rest of your preamble and document...

% \documentclass[10pt]{article} %Sets the default text size to 11pt and class to article.
%------------------------Dimensions--------------------------------------------
\pagenumbering{gobble}% Remove page numbers (and reset to 1)
\topmargin=-20pt %length of margin at the top of the page (1 inch added by default)
\oddsidemargin=0.0in %length of margin on sides for odd pages
\evensidemargin=0in %length of margin on sides for even pages
\textwidth=6.7in %How wide you want your text to be
\marginparwidth=0.5in
\headheight=0pt %1in margins at top and bottom (1 inch is added to this value by default)
\headsep=0pt %Increase to increase white space in between headers and the top of the page
\textheight=9.5in %How tall the text body is allowed to be on each page

% \usepackage{xcolor}
\usepackage[table]{xcolor} % Make sure it's included, possibly already there for linkcolor

\definecolor{linkcolor}{RGB}{32,121,199}
\definecolor{textcolor}{HTML}{333333} % Define the base text color

\AtBeginDocument{\color{textcolor}} % Set the default text color for the document

\definecolor{linkcolor}{RGB}{32,121,199}

\usepackage[utf8]{inputenc}
\usepackage[colorlinks=true,urlcolor=linkcolor]{hyperref}

\newcommand\tab[1][1cm]{\hspace*{#1}}
\newcommand\smallspace[1][0.23cm]{\hspace*{#1}}
\newcommand\negativespace[1][-0.12cm]{\hspace*{#1}}

%\usepackage[T1]{fontenc}
%\usepackage{libertine}


\begin{document}

\centerline{{\LARGE \bf Jaques Grobler, B.Eng.}}
\centerline{\href{mailto:jaquesgrobler@gmail.com}{jaquesgrobler@gmail.com}}


\noindent %Prevents the following text from being indented
\\\\
\vspace*{-6pt}
{\negativespace \Large \bf Recent Professional Experience}\\
\line(1,0){485}
\\
\noindent

\noindent
{\bf Senior Full-Stack Engineer}, \textit{employee at \href{https://www.omicronenergy.com/de/}{Omicron Electronics GmbH}}  \hfill \textit{Feb 2022 - Present}
\begin{itemize}
\setlength\itemsep{0.05em}
\item Development of a central management system for smart intrusion detection sensors installed \hfill Klaus, Austria \\
in control centers, power plants and substations, focusing on high availability, security, \\
and performance.
\item Designed and implemented full-stack solutions using \textbf{Typescript}, \textbf{React}, \textbf{Deno/Node.js}, \\
\textbf{PostgreSQL}, \textbf{RabbitMQ} and \textbf{Keycloak}, with a strong emphasis on dockerized \\
microservices communicating through AMQPS, and Grafana for data visualization.
\item Required close-collaboration with engineers and developers of the existing sensors.
\item Additional Responsibility in interteam weekly cyber-security vulnerability audits, some \\
 SCRUM activities and assisting release planning.
\end{itemize}

\noindent
{\bf Senior Software Engineer}, \textit{employee at \href{https://anyline.com}{Anyline GmbH}}  \hfill \textit{Nov 2019 -- Jan 2022}
\begin{itemize}
\setlength\itemsep{0.05em}

\item Led frontend development for a platform focused on OCR data collection, annotation, \hfill Vienna, Austria \\
machine learning model training, and deployment using \textbf{Typescript}, \textbf{React}, and \textbf{Nestjs}.
\item Collaborated with the UX team on frontend design and technical implementation.
\item Implemented and managed Identity and Access Management (IAM) using \textbf{Keycloak} \\
and \textbf{Auth0}, which involved creating a custom user-management portal \\
to support the platform.
\item Assisted in the preparation and implementation changes obtaining ISO27001 \\
certification.
\item Developed the frontend team through in training, recruiting/interviewing \\
and mentoring.

\end{itemize}

\noindent
{\bf Senior Software Engineer}, \textit{employee at \href{https://vulcanlabs.com/}{Vulcan Labs}}  \hfill \textit{Jun 2017 -- Nov 2019}
\begin{itemize}
\setlength\itemsep{0.05em}

\item Responsible for development and maintenance of internal products \hfill Cape Town, South Africa \\
as well as contracting for external clients, ranging from building \textbf{React} front-end \\
tools from the ground up to maintaining legacy codebases in \textbf{Java}.
\item \textbf{Contract work includes:}
  \begin{itemize}
    \item \textbf{Sewells Group} - Maintained and expanded a large automotive administration \\
    tool built in \textbf{Java}, and built new dashboarding tools in \textbf{React}.
    \item \textbf{Xneelo (formerly Hetzner SA)} - Front-end development of several tools ranging \\
    from DNS management and mail administration to customer product management \\
    using \textbf{React}, with some backend \textbf{Ruby} work.
    \item \textbf{Chaufher} - Team lead and technical consultant for a Cape Town Transport \\
    provider startup.
  \end{itemize}
\end{itemize}

\noindent
{\bf Solutions Architect}, \textit{employee at \href{https://www.kurtosys.com/}{Kurtosys Systems}}  \hfill \textit{Oct 2016 -- Jun 2017}
\begin{itemize}
\setlength\itemsep{0.05em}
\item Development of \textbf{Typescript/React} based embeddable tools for asset \hfill Cape Town, South Africa \\
management and investment sites in the FinTech industry.
\end{itemize}

\noindent
{\bf Software Engineer}, \textit{employee at \href{https://energypartners.co.za/}{Energy Partners}}  \hfill \textit{Apr 2014 -- Oct 2016}
\begin{itemize}
\setlength\itemsep{0.05em}
\item Development of business intelligence and dashboarding services for electrical \hfill Cape Town, South Africa \\
engineering data using \textbf{Python/Django} with a MongoDB database.
\item Development of residential-solar product data-warehousing, device-data \\
ingestion, API and a commissioning-webapp for field services engineers in React.

\end{itemize}

\noindent
{\bf Research Engineer}, \textit{employee at \href{https://www.inria.fr/en}{INRIA}}  \hfill \textit{Jan 2012 -- Jan 2014}
\begin{itemize}
\setlength\itemsep{0.05em}

\item Dedicated engineer on \href{https://scikit-learn.org/stable/}{scikit-learn} machine learning library in scientific Python, \hfill Saclay, France \\
website building and community support.
\item Research engineer to Team Parietal of INRIA to assist processing neuroscience data.

\end{itemize}

\noindent
{\bf Project Management Assistant (Part-time)}, \textit{employee at Housing Solutions}  \hfill \textit{Apr 2010 -- Feb 2011}
\begin{itemize}
\setlength\itemsep{0.05em}
\item Assistant to project management, settlement models, research and administration \hfill Stellenbosch, South Africa \\
using Python.

\end{itemize}

\noindent
{\bf Junior Developer (Part-time)}, \textit{employee at Catchword Technologies}  \hfill \textit{Oct 2009 -- Jan 2011}
\begin{itemize}
\setlength\itemsep{0.05em}

\item Working on Pattern Recognition Library – optimization of existing algorithms and \hfill Stellenbosch, South Africa \\
utilities development using C++ and the scientific Python libraries.

\end{itemize}

\noindent %Prevents the following text from being indented
\\
\vspace*{-6pt}
{\negativespace \Large \bf Education}\\
\line(1,0){485}\\
\\
\noindent
{\bf Masters of Electrical & Electronic Engineering - \textit{discontinued}} \hfill \textit{2012} \\
\textit{Stellenbosch University (Thesis: Optimising a phoneme recogniser based on logistic regression [C++, Python, Matlab])} \\\\
\noindent
{\bf Bachelor of Electrical & Electronic Engineering with Computer Sciences} \hfill \textit{2008} \\
\textit{Stellenbosch University (Thesis: FPGA Implementation of Digital Audio Filters [VHDL, Matlab])} \\
\\
\\
\vspace*{-6pt}
{\negativespace \Large \bf Publications}\\
\line(1,0){485}\\
{\bf \href{https://paperswithcode.com/paper/api-design-for-machine-learning-software}{API design for machine learning software: experiences from the scikit-learn project}} \hfill \textit{September 2013} \\
\\

\noindent
{\bf Languages:} \smallspace Native Speaker: English, Afrikaans. \\
\tab \tab Strong Professional Proficiency: Spanish, German. \\
\tab \tab Limited Professional Proficiency: French \\ \\
\noindent
{\bf Technologies:} \textbf{Node.JS, Typescript, React, SQL, Docker,}\\
\tab \tab\ Nextjs, Deno, Keycloak, Lit, Java, Python, Nextjs, RabbitMQ, Auth0

\end{document}
